### 2022-05-24 main/chapter_2ljets.tex
add descriptions of muon and electron id

There are certain plots and tables which, personally, I first seek when
meeting an \atlas\ search paper.
This chapter begins by presenting those results in brief in
Section~\ref{sec:2ljets_splash}.
The the meat of this chapter (or if you prefer, its gory details) follows in
Section~\ref{sec:2ljets_context} onwards.

@@

In short, all triggers require $\pt^{\ell_i}$ values to exceed thresholds in
the range $8\textrm{--}26~\eV[G]$.
To detail all trigger requirements and their variations with data period
would be too tedious and not enlightening, but their $\pt^{\ell_i}$ requirements
are summarized here.
\begin{itemize}
\item Electron pair: requirements vary between
\begin{itemize}
\item $\pt^{e_2} > 12~\eV[G]$ and
\item $\pt^{e_2} > 17~\eV[G]$.
\end{itemize}
\item Muon pair: various requirements include
\begin{itemize}
\item $\pt^{\mu_2} > 10~\eV[G]$,
\item $\pt^{\mu_2} > 14~\eV[G]$,
\item $\pt^{\mu_1} > 18~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$, and
\item $\pt^{\mu_1} > 22~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$.
\end{itemize}
\item Emu pair: various asymmetric requirements include
\begin{itemize}
\item $\pt^{e_1} > 17~\eV[G]~\&~\pt^{\mu_1} > 14~\eV[G]$,
\item $\pt^{e_1} > 7~\eV[G]~\&~\pt^{\mu_1} > 24~\eV[G]$, and
\item $\pt^{e_1} > 26~\eV[G]~\&~\pt^{\mu_1} > 8~\eV[G]$.
\end{itemize}
\end{itemize}
Trigger requirements increase in hardness with time.

@@

The benefit of an additional trigger could be increased signal yields, if that
trigger do not also harmfully increase inseparable backgrounds.
A study, \textit{which was performed by Knut Vadla}, compared the efficiencies
of including one-lepton triggers.
In a signal-region-like selection requiring two leptons, two jets and
$\met > 200~\eV[G]$, this study showed that two-lepton triggers already accept
in excess of $90\%$ of events from benchmark C1N2 models.

Therefore, any additional trigger has at most a $\approx10\%$;
improvement. Adding one-lepton triggers was found to increase efficiency by
only a few percentage points, depending on the model.
We considered that to be too little.

@@

\subsection{Leptons}
Charged leptons are essential to the $\twoljets$ analysis.

>>>>

There are certain plots and tables which, personally, I first seek when
meeting an \atlas\ search paper.
This chapter begins by presenting those results in brief in
Section~\ref{sec:2ljets_splash}.
The meat of this chapter (or if you prefer, its gory detail) follows in
Section~\ref{sec:2ljets_context} onwards.

@@

In short, all triggers require $\pt^{\ell_i}$ values to exceed thresholds in
the range $8\textrm{--}26~\eV[G]$.
To detail all trigger requirements and their variations with data period
would be too tedious and not enlightening, but their $\pt^{\ell_i}$ requirements
are summarized here.
\begin{itemize}
\item Electron pair: requirements vary between
\begin{itemize}
\item $\pt^{e_2} > 12~\eV[G]$ and
\item $\pt^{e_2} > 17~\eV[G]$.
\end{itemize}
\item Muon pair: various requirements include
\begin{itemize}
\item $\pt^{\mu_2} > 10~\eV[G]$,
\item $\pt^{\mu_2} > 14~\eV[G]$,
\item $\pt^{\mu_1} > 18~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$, and
\item $\pt^{\mu_1} > 22~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$.
\end{itemize}
\item Emu pair: various asymmetric requirements include
\begin{itemize}
\item $\pt^{e_1} > 17~\eV[G]~\&~\pt^{\mu_1} > 14~\eV[G]$,
\item $\pt^{e_1} > 7~\eV[G]~\&~\pt^{\mu_1} > 24~\eV[G]$, and
\item $\pt^{e_1} > 26~\eV[G]~\&~\pt^{\mu_1} > 8~\eV[G]$.
\end{itemize}
\end{itemize}
Quite generally throughout the data used in $\twoljets$, trigger requirements
have increased in hardness with time.

@@

The benefit of an additional trigger could be in increased signal yields if
that trigger do not also harmfully increase inseparable backgrounds.
A study, \textit{which was performed by Knut Vadla}, investigated the effects
of of including one-lepton triggers.
In a signal-region-like selection requiring two leptons, two jets and
$\met > 200~\eV[G]$, this study showed that two-lepton triggers already accept
in excess of $90\%$ of events from benchmark C1N2 models.
Therefore, any additional trigger has at most a $\approx10\%$;
improvement. Adding one-lepton triggers was found to increase efficiency by
only a few percentage points, depending on the model.
We considered that to be too little to be worthwhile.

@@

\subsection{Leptons}
In the context of $\twoljets$, `leptons' means `electron-or-muons';
this is because taus, which decay before reconstruction, and are not used
directly in $\twoljets$, and neutral leptons (the neutrinos) go missing.

Reconstructed lepton objects feature momenta, charges, and flavours.
Each is included only if it satisfies certain kinematic and
is identified with certain `quality' requirements.

Muons are identified by fitting tracks to hits in the inner tracker and muon
spectrometer, and their quality requirements use goodness-of-fit metrics of
those fits along with low level details of detector interactions, to primarily
to reduce backgrounds from non-prompt muons from hadronic
decays~\cite{atlas_muon_quality_MUON_2018_03}.

Electron identification combines data from the inner tracker and
calorimeters. Electron quality criteria use numerous features of detector
interactions, track fitting metrics, matching of those tracks to calorimeters,
calorimeter shower shapes, and leakage into the hadronic calorimeter to reduce
backgrounds from photons, hadrons, and non-prompt electrons from hadronic
decays~\cite{atlas_egamma_quality_EGAM_2018_01}.

\TODO{signal objects have isolation criteria}

\TODO{lepton pairs SF-OS for Z}
